\documentclass{resume}

\usepackage[left=0.75in,top=0.3in,right=0.75in,bottom=0.6in]{geometry} % Document margins

\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}}
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}


\name{Abdelsalam ElTamway}
\address{30, ElTayaran St., Nasr City, Cairo, Egypt}
\address{(+02)01003435365 \\ solomspd@aucegypt.edu}

\begin{document}
\begin{small}
	
	\begin{rSection}{Education}
		{\bf The American University in Cairo (AUC)} \hfill {\em 2017-2023} \\
		BSc in Computer Engineering. BSc in Electronics Engineering GPA: 3.63\\
		{\bf International School for Elite Education (ISEE)} \hfill {\em 2011-2017}
		\\ IGCSE. Graduated with honors.
	\end{rSection}
	
	\begin{rSection}{Technical Skills}
		\begin{itemize}
			\itemsep-0.5em
			\item Versed in C++, Python, kotlin, Java, Node.js, PHP, SQL, mongoDB, Verilog and HTML.
			\item Experienced with circuit design with Eagle and Altium.
			\item Experienced with Arduino and Raspberry Pi.
			\item Built autonomous vacuuming robot featuring a gripping hand.
			\item Experienced 3D printing enthusiast.
			\item Programmed various games and applications, including a fully featured version of pac man, mostly in the language C++.
			\item PC enthusiast, build my own liquid cooled computer.
		\end{itemize}
	\end{rSection}
	
	\begin{rSection}{Experience}
		\begin{itemize}
			\itemsep-0.5em
			\item Work as a teaching assistant at university for the first 3 levels of computer science.
			\item Organising member of local univeristy ACM.
			\item Maintian ACM scoreboard application used by unversity.
		\end{itemize}
	\end{rSection}
	\begin{rSection} {Extracurricular Activities}
		{\bf Particiaped in the ICPC ACM} \hfill {\em 2019} \\
		After gaining experience and pratice of competitive programing, entered the local ICPC ACM achieved $10^{th}$ place out of 26. \\
		{\bf Participated in the Code Geist hackathon } \hfill {\em 2019} \\
		Entered with a team of to build an app and its pitch in 48 hours. Created an environment centric mobile apoplication meant to encourage and rewards individuals for collecting litter.\\
		{\bf ROV electronics memeber} \hfill {\em 2017-2019} \\
		Part of the univeristy's Remotely Operated Vehicle (ROV) team that participated in the international MATE competition. Greatly contibuted to ciruit design and mechanical design. \\
		{\bf ROV Multimedia Head, Robotics Club, AUC} \hfill {\em 2017-2019} \\
		Led team of 5 to market and document ROV events. Photographed and filmed dozens of events. Filmed and edited 4 videos for marketing purposes. Designed brochures to advertise robotics classes.
		% {\bf Multimedia Member Literature Club, AUC} \hfill {\em 2018-2019} \\
		% Photographed 3 events and created posters for marketing purposes.\\
		{\bf Recreational Scuba Diver, Scuba Diving, Independent} \hfill {\em 2009-present}\\
		Licensed 2-star CMAS scuba diver. Preformed over 100 scuba dives in the Red Sea.\\
		% {\bf Multimedia Member Peer Leader Advising (PAL), AUC} \hfill {\em 2018}\\
		% Photographed half a dozen events. Created 3 animated and heavily edited videos officially published by University.\\
		{\bf Assistant Multimedia Head, AUC Insider, AUC} \hfill {\em 2017}\\
		Photographed dozens of events. Published over a dozen photographs in the University newspaper.\\
		{\bf Camper, NASA Camp, Independent} \hfill {\em 2015}\\
		Attended NASA camp in Atlanta, USA. Won “Best Camper” award.\\
		{\bf Contestant, Science fair, Student Expo 2014} \hfill {\em 2014} \\
		Won first place at the high school level with a 4 wheeled remote controlled drone featuring a 3-axis arm.
		
	\end{rSection}
	
	\begin{rSection}{Skills}
		\begin{enumerate}
			\itemsep -0.5em
			\item Very fluent in written and spoken English and Arabic.
			\item Professional Photographer
			\item Proficient in Adobe After Effects, Premier Pro, Photoshop, Illustrator, InDesign, Autodesk 3Ds MAX and Blender.
		\end{enumerate}
	\end{rSection}
	\begin{rSection}{Travel}
		Travelled to most of Europe, the U.S.A, the Middle east and Africa
	\end{rSection}
\end{small}
	\end{document}