\documentclass{resume}

\usepackage[left=12mm,top=12mm,right=12mm,bottom=12mm]{geometry} % Document margins

\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}}
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}


\name{Abdelsalam ElTamway}
\address{30, ElTayaran St., Nasr City, Cairo, Egypt}
\address{(+02)01003435365 \\ solomspd@aucegypt.edu \\ github.com/solomspd \\ linkedin.com/in/abdelsalam-et/}

\begin{document}
\begin{small}
	
	\begin{rSection}{Education}
		{\bf The American University in Cairo (AUC)} \hfill {\em 2017-2023} \\
		BSc in Computer Engineering. BSc in Electronics Engineering. GPA: 3.64/4.0\\
		{\bf International School for Elite Education (ISEE)} \hfill {\em 2011-2017}\\
		IGCSE. Graduated with high honors.
	\end{rSection}
	
	\begin{rSection}{Technical Skills}
		\begin{itemize}
			\itemsep-0.4em
			\item Versed in C++, Python, kotlin, Java, Javascript, PHP, SQL, MongoDB, Verilog, Latex, CSS and HTML.
			\item Experienced in circuit design with Eagle and Altium.
			\item Experienced with Arduino and Raspberry Pi.
			\item Robot enthusiast. Built several robots, including a cleaning vacuuming robot with a gripper arm.
			\item Experienced 3D printing enthusiast; designed and printed dozens of my own robotics components and personal projects.
			\item Programmed various games and applications, including a fully featured version of pac man, a text compression tool and a circuit netlist generator for boolean expressions; mostly in the language C++.
			\item PC enthusiast, built my own liquid cooled computer. Built and setup file ,surveillance, DNS and a game servers.
		\end{itemize}
	\end{rSection}

	\begin{rSection}{Competitions}
		{\bf Participant, International Collegiate Programming Contest, AUC} \hfill {\em 2019} \\
		Entered the local ICPC ACM after gaining experience and practice in competitive programing; achieving $9^{th}$ place out of 14. \\
		{\bf Participant, Code Geist hackathon, Sefr Wahed} \hfill {\em 2019} \\
		Created an app and it's pitch in 48 hours with a team of 4; developed an environment centric mobile application meant to encourage and reward individuals for collecting litter.\\
		{\bf ROV electronics member, Robotics Club, AUC} \hfill {\em 2017-2019} \\
		Entered with the university's Remotely Operated Vehicle (ROV) team that participated in the international MATE competition; Greatly contributed to circuit design and mechanical design. \\
		{\bf Contestant, Science fair, Student Expo 2014} \hfill {\em 2014} \\
		Won first place at the high school level with a 4 wheeled remote controlled robot featuring a 3-axis arm.
	\end{rSection}
	
	\begin{rSection}{Experience}
		{\bf Tutor, Computer Science and Engineering Clinic, AUC} \hfill {\em 2019-present} \\
		Tutor of the student driven computer science and engineering "clinic"; an organization that is meant to provide the support to students of the first 4 levels of computer science and engineering through sessions and one on one tutoring sessions.\\
		{\bf Undergraduate teaching assistant, Programming fundamentals, AUC} \hfill {\em 2018-2019} \\
		Worked as an undergraduate teaching assistant for the second level of computer engineering; helping students understand programming concepts; Also maintained ACM scoreboard used by university.
	\end{rSection}
	\begin{rSection} {Extracurricular Activities}
		{\bf Recreational Scuba Diver, Scuba Diving, Independent} \hfill {\em 2009-present}\\
		Licensed 2-star CMAS scuba diver; preformed over 100 scuba dives in the Red Sea.\\
		{\bf ROV Multimedia Head, Robotics Club, AUC} \hfill {\em 2017-2019} \\
		Led team of 5 to market and document ROV events. Photographed and filmed dozens of events. Filmed and edited 4 videos for marketing purposes. Designed brochures to advertise robotics classes. Gained more experience on how to lead\\
		% {\bf Multimedia Member Literature Club, AUC} \hfill {\em 2018-2019} \\
		% Photographed 3 events and created posters for marketing purposes.\\
		{\bf Multimedia Member Peer Leader Advising (PAL), AUC} \hfill {\em 2018}\\
		Photographed half a dozen events. Created 3 animated and heavily edited videos officially published by University.\\
		{\bf Assistant Multimedia Head, AUC Insider, AUC} \hfill {\em 2017}\\
		Photographed dozens of events. Published over a dozen photographs in the University newspaper.\\
		{\bf Camper, NASA Camp, Independent} \hfill {\em 2015}\\
		Attended NASA camp in Atlanta, USA. Won “Best Camper” award.\\
		
	\end{rSection}
	
	\begin{rSection}{Skills}
		\begin{itemize}
			\itemsep -0.4em
			\item Very fluent in written and spoken English and Arabic.
			\item Professional Photographer.
			\item Proficient in Adobe After Effects, Premier Pro, Photoshop, Illustrator, InDesign, Autodesk 3Ds MAX and Blender.
		\end{itemize}
	\end{rSection}
	\begin{rSection}{Travel}
		Travelled to most of Europe, the U.S.A, the Middle east and Africa
	\end{rSection}
\end{small}
	\end{document}