\documentclass{resume}

\newcommand{\email}{abdelsalam@solom.dev}

\begin{document}

\begin{tabularx}{\textwidth}{X|r}
	
	{\LARGE\MakeUppercase{\bf Abdelsalam ElTamawy}}
	% {\small\href{https://www.youtube.com/watch?v=8wwv_bj3Hvc}{Self Introduction Video \iconin{\faYoutubePlay}}}
	&
	\small{
		\begin{tabular}{ll}
			\href{mailto:\email}{\iconanot{\faEnvelope}{\email}} & \href{https://solom.dev}{\iconanot{\faGlobe}{solom.dev}} \\
			\href{https://github.com/solomspd}{\iconanot{\faGithub}{github.com/solomspd}} & \href{tel:+201003435365}{\iconanot{\faPhone}{(+20)1003435365}} \\
			\href{https://linkedin.com/in/abdelsalam-et}{\iconanot{\faLinkedin}{/in/abdelsalam-et}} & \iconanot{\faMapMarker}{Nasr City, Cairo, Egypt} \\
		\end{tabular}
	}

\end{tabularx}

\begin{rsection}{\MakeUppercase{about me} \hfill \href{https://www.youtube.com/watch?v=8wwv_bj3Hvc}{Self Introduction Video \iconin{\faYoutubePlay}}}{}{}
	As a highly motivated computer engineer, I am confident in my skills in software development and academic research proving valuable to any team.
	% I am a highly motivated computer engineer seeking to purposefully contribute who leads by example.
	Seeking to Create tailored solutions to novel problems.
\end{rsection}

\begin{minipage}[t]{0.54\textwidth}

	\begin{rsection}{\MakeUppercase{education}}{smallpreskip}

		\begin{rcontent}{The American University in Cairo (AUC)}{2017-2022}{}{Cairo}
			\begin{itemize}
				\item BSc in Computer Engineering
				\item Graduated with High Honors. GPA: 3.6/4.0
			\end{itemize}
		\end{rcontent}

	\end{rsection}

	\begin{rsection}{\MakeUppercase{selected projects}}{}

		\begin{rcontent}{\href{https://github.com/solomspd/senior-project}{Machine learning based decompiler \gitsep \iconin{\faGithub}}}{2021-2022}{}{}
		\begin{techtag}
			\item \techitem{Python}
			\item \techitem{Pytorch}
			\item \techitem{Graph ML}
			\item \techitem{Anaconda}
		\end{techtag}
			\begin{itemize}
				\item Led team of 6 to create a transformer-based decompiler targeting Android.
				\item Novel tree graph generator for AST representation.
				\item Designed to be a forensic malware tool.
			\end{itemize}
		\end{rcontent}
		\divider
		\begin{rcontent}{\href{https://github.com/solomspd/POV-fan-display}{Persistance of vision display \gitsep \iconin{\faGithub}}}{2021}{}{}
		\begin{techtag}
			\item \techitem{Embedded}
			\item \techitem{C}
			\item \techitem{STM32}
			\item \techitem{ESP32}
			\item \techitem{HAL}
			\item \techitem{ESP-IDF}
		\end{techtag}
			\begin{itemize}
				\item Created high-speed fan display and embedded system to fulfill microsecond timing constraints.
				\item Featured embedded web server for user accessibility and customization.
			\end{itemize}
		\end{rcontent}
		\divider
		\begin{rcontent}{\href{https://github.com/solomspd/solom-ML-lib}{Machine learning library from scratch \gitsep \iconin{\faGithub}}}{2021}{}{}
		\begin{techtag}
			\item \techitem{Python}
			\item \techitem{CUDA}
			\item \techitem{Deep NN}
			\item \techitem{CNN}
		\end{techtag}
			\begin{itemize}
				\item Created CUDA accelerated ML library.
				\item Implemented training and inference framework for deep neural networks and convolutional neural networks.
			\end{itemize}
		\end{rcontent}
		\divider
		\begin{rcontent}{\href{https://github.com/solomspd/ultrasonic-sensor}{Distance sensor from scratch \gitsep \iconin{\faGithub}}}{2021}{}{}
		\begin{techtag}
			\item \techitem{Embedded}
			\item \techitem{C}
			\item \techitem{STM32}
		\end{techtag}
			\begin{itemize}
				\item Built ultrasonic distance sensor with 1mm accuracy.
				\item Reverse-engineered market boards to create a more accurate sensor.
			\end{itemize}
		\end{rcontent}
		\divider
		\begin{rcontent}{\href{https://github.com/solomspd/RISC-V-CPU}{RISC-V microarchitecture \hspace{0.25em} \iconin{\faGithub}}}{2021}{}{}
		\begin{techtag}
			\item \techitem{Verilog}
			\item \techitem{RISC-V ASM}
			\item \techitem{Xillinix FPGA}
		\end{techtag}
			\begin{itemize}
				\item Implemented 6 pipeline RISC-V microarchitecture on an FPGA in Verilog fulfilling specification requirements.
				\item Compiled and ran C programs on FPGA using microarchitecture.
			\end{itemize}
		\end{rcontent}
		\divider
		\begin{rcontent}{\href{https://github.com/solomspd/pacman}{Pacman clone \hspace{0.25em} \iconin{\faGithub}}}{2018}{}{}
		\begin{techtag}
			\item \techitem{C++}
			\item \techitem{OOP}
			\item \techitem{SFML}
		\end{techtag}
			\begin{itemize}
				\item Recreated first 3 levels of Pacman.
				\item Complete with level editor and online user scoreboard.
			\end{itemize}
		\end{rcontent}

	\end{rsection}

\end{minipage}
\hfill
\begin{minipage}[t]{0.45\textwidth}

	\begin{rsection}{\MakeUppercase{experience}}{smallpreskip}
		\begin{rcontent}{Founding Engineer}{2022-present}{\href{https://lensed.app/}{Lensed}}{San Francisco, USA (remote)}
		\begin{itemize}
			\item Led engineering team of 4 to create novel solutions to develop engineer-focused tools enabling EDA design debugging.
			\item Architected and implemented CAD circuit data pipelines that outperform industry solutions.
			\item Engineered novel data representation using Rust and Python to seamlessly integrate into toolchains, complying with industry standards.
			\item Worked closely with industry experts to fulfill interdisciplinary requirements.
			\item Deployed CI/CD pipeline and delivered production hybrid cloud deployments to customers.
			\item Leveraged LLMs and novel AI models to provide augmented insights to engineers.
		\end{itemize}
		\end{rcontent}
		\divider
		\begin{rcontent}{Graduate teaching assistant}{2022-present}{AUC}{Cairo, Egypt}
			\begin{itemize}
				\item Taught CUDA and parallel programming concepts to students in GPU computing course.
				\item Covered advanced concepts including RDMA.
				\item Orchestrated deployment of docker environment.
			\end{itemize}
		\end{rcontent}
		\divider
		\begin{rcontent}{Undergraduate teaching assistant}{}{AUC}{Cairo, Egypt}
			\begin{itemize}
				\item Assembly\&Comp. Organization \calstick{2021-2022}
				\item Computer Architecture \calstick{2020-2021}
				\item Department Tutor \calstick{2019-2020}
				\item Programming Fundamentals \calstick{2018-2020}
			\end{itemize}
		\end{rcontent}
		\divider
		\begin{rcontent}{Lead research assistant}{2020-2021}{AUC}{Cairo, Egypt}
			\begin{itemize}
				\item Led a team of 4 to create a process that builds application-specific RISC-V-based CPUs.
			\end{itemize}
		\end{rcontent}
		\divider
		\begin{rcontent}{AI development intern}{2020-2021}{\href{https://www.tod-z.com/}{Tod-Z}}{Talin, Estonia (remote)}
			\begin{itemize}
				\item Led AI and machine learning development.
				\item Built entire machine learning stack from concept to training to deployment on AWS.
			\end{itemize}
		\end{rcontent}
		\divider
		\begin{rcontent}{Intern}{2020}{\href{https://www.agiletz.com/}{Agile tech.}}{Netherlands (remote)}
			\begin{itemize}
				\item Built web store using OutSystems.
				\item Regularly communicated for quality assurance.
			\end{itemize}
		\end{rcontent}

	\end{rsection}


\end{minipage}

\begin{minipage}[t]{0.49\textwidth}

	\begin{rsection}{\MakeUppercase{extracurricular}}{}

		\begin{rcontent}{ROV media head}{2017-2019}{AUC}{Cairo, Egypt}
			\begin{itemize}
				\item Led team of 5 to market and document Robotics club's remotely operated vehicle events.
				\item Photographed and documented dozens of events and directed 4 marketing videos.
			\end{itemize}
		\end{rcontent}
		\divider
		\begin{rcontent}{Assistant media head}{2017}{AUC insider}{}airo, Egypt
			\begin{itemize}
				\item Lead photographer for AUC newspaper.
				\item Published over a dozen photographs covering local events.
			\end{itemize}
		\end{rcontent}
		\divider
		\begin{rcontent}{NASA camp}{2015}{NASA}{Atlanta, USA}
			\begin{itemize}
				\item Won \say{Best Camper} award.
			\end{itemize}
		\end{rcontent}

	\end{rsection}

	\begin{rsection}{\MakeUppercase{publications}}{}

		\begin{rcontent}{A Neural Generation Framework for Android Decompilation (Abdelsalam, et al.)}{2022}{(pending publication)}{}
			\begin{itemize}
				\item Completed Bachelor thesis
				\item Created a novel method for tree graph generation.
				\item Applied the novel method and transformer translation to Android decompilation.
			\end{itemize}
		\end{rcontent}
		\divider
		\begin{rcontent}{\href{https://businessmonthlyeg.com/wp-content/uploads/2022/08/August-2022.pdf\#page=35}{Dive, Eat, Sleep \& Repeat}}{2022}{Busniess Monthly Magazine}{}
			\begin{itemize}
				\item Wrote an article on diving in the Red Sea during shark season.
				\item Released in the 2022 August issue of Business Monthly.
			\end{itemize}
		\end{rcontent}
		\divider
		\begin{rcontent}{Application specific CPU optimizer}{2020-2022}{}{}
			\begin{itemize}
				\item Worked on a framework to optimize unused hardware in HDL according to application use case.
				\item Led team of 3 to create FPGA focused optimization framework focused on RISC-V CPUs.
			\end{itemize}
		\end{rcontent}

	\end{rsection}

	\begin{rsection}{\MakeUppercase{programming languages}}{}
		\renewcommand{\arraystretch}{1.25}
		\begin{tabular}{ccc}
			\lang{Python} & \lang{C++} & \lang{Rust} \\
			\lang{C} & \lang{\LaTeX} & \lang{Verilog} \\
			\lang{Kotlin} & \lang{Dart} & \lang{Javascript} \\
			\lang{Bash} & \lang{SQL} & \\
		\end{tabular}
	\end{rsection}

\end{minipage}
\hfill
\begin{minipage}[t]{0.49\textwidth}

	\begin{rsection}{\MakeUppercase{competitions}}{}

		\begin{rcontent}{HackTrick Hackathon}{2022}{DELL EMC}{Cairo, Egypt}
			\begin{itemize}
				\item Built a reinforcement learning model to compete in material pipeline optimization challenges.
			\end{itemize}
		\end{rcontent}
		\divider
		\begin{rcontent}{ICPC ACM}{2019}{AUC}{Cairo, Egypt}
			\begin{itemize}
				\item Entered local ICPC ACM.
				\item Was the youngest participant.
			\end{itemize}
		\end{rcontent}
		\divider
		\begin{rcontent}{Code Geist Hackathon}{2019}{Sefr Wahed}{Cairo, Egypt}
			\begin{itemize}
				\item Created an app and its pitch in 72 hours.
				\item Collaborated in a team of 4.
				\item Developed a platform to address littering.
			\end{itemize}
		\end{rcontent}
		\divider
		\begin{rcontent}{MATE ROV}{2017-2019}{MATE}{Cairo, Egypt}
			\begin{itemize}
				\item Joined university's Remotely Operated Vehicle team.
				\item Contributed to circuit and mechanical design.
			\end{itemize}
		\end{rcontent}
		\divider
		\begin{rcontent}{Science Fair}{2014}{Student Expo}{Cairo, Egypt}
			\begin{itemize}
				\item Won first place at high school level with a 4-wheeled remote-controlled robot featuring a 3-axis arm.
			\end{itemize}
		\end{rcontent}
	\end{rsection}

	\begin{rfloat}{\MakeUppercase{skills}}
		\begin{techlist}
			\item \techitem{Git VCS}
			\item \techitem{Linux}
			\item \techitem{Docker}
			\item \techitem{DevOps}
		\end{techlist}
	\end{rfloat}

	\begin{rfloat}{\MakeUppercase{languages}}
		\begin{techlist}
			\item \techitem{English (native)}
			\item \techitem{Arabic (native)}
		\end{techlist}
	\end{rfloat}

	\begin{rsection}{\MakeUppercase{hobbies}}{}

		\begin{rcontent}{Recreational scuba diver}{}{}{}
			\begin{itemize}
				\item Licensed 2-star CMAS scuba diver.
				\item Over 200 dives in the Red Sea since 2009.
			\end{itemize}
		\end{rcontent}
		\divider
		\begin{rcontent}{PC enthusiast}{}{}{}
			\begin{itemize}
				\item Built own liquid-cooled computer.
				\item Administering home-lab with file, surveillance, and DNS servers.
			\end{itemize}
		\end{rcontent}
		\divider
		\begin{rcontent}{3D printing enthusiast}{}{}{}
			\begin{itemize}
				\item Designed own 3D printed robot components.
			\end{itemize}
		\end{rcontent}
		\divider
		\begin{rcontent}{Travel}{}{}{}
			\begin{itemize}
				\item Traveled to most of Europe, the U.S.A, the Middle East and Africa
			\end{itemize}
		\end{rcontent}

	\end{rsection}

	
\end{minipage}

\end{document}